Vegetation Change Assessment - SOD Plots in Sonoma County

### 2016-03-22 veg-change-assessment.Rmd
Update variable names.

# Overstory species data of tagged and untagged stems
tag_dbh_plot <- as.tbl(read.csv("analysis/data/tag-dbh-plot.csv"))
tag_dbh_plot
tag_dbh_plot$plotid <- tolower(tag_dbh_plot$plotid)
tag_dbh_plot$species <- tolower(tag_dbh_plot$species)

tag_dbh_stem <- as.tbl(read.csv("analysis/data/tag-dbh_0514-corrected.csv"))
tag_dbh_stem
tag_dbh_stem$plotid <- tolower(tag_dbh_stem$plotid)
tag_dbh_stem$species <- tolower(tag_dbh_stem$species)

alt_dbh_plot <- as.tbl(read.csv("analysis/data/alt-dbh-plot.csv"))
alt_dbh_plot

alt_dbh_stem <- as.tbl(read.csv("analysis/data/alt-species-dbh-corrected.csv"))
alt_dbh_stem

all_stems <- as.tbl(read.csv("analysis/data/all_stems_corrected.csv"))
summary(all_stems)
      # rbind(select(tag_dbh_stem, plotid, species, dbh, status, year),
      #             alt_dbh_stem)
all_stems$plotid <- as.factor(all_stems$plotid)
all_stems$status <- as.factor(all_stems$plotid)
all_stems$year <- as.factor(all_stems$year)

@@

```{r recalculate plot data, echo=F}
# Recalculate tag-dbh-plot to exclude new large dead quag stem in 2014 at sugar05
filter(tag_dbh_stem, plotid == "sugar05", year == 2014)
tag_dbh_plot <- tag_dbh_stem %>% 
      filter(dbh >= 2.0, tag != 7794) %>% 
      group_by(plotid, species, year, status, location) %>% 
      summarise(avg_ba_m2 = mean(pi*dbh^2/40000, na.rm = T), 
                tot_ba_m2 = sum(pi*dbh^2/40000, na.rm = T),
                abundance = length(dbh))
tag_dbh_plot <- ungroup(tag_dbh_plot)

# Overstory species w/measured DBH rooted in the plot
os_dbh_in_plot <- rbind(
      tag_dbh_plot %>% filter(location == "In") %>% 
            select(plotid, species, status, year, everything(), -location), 
      select(alt_dbh_plot, -tot_dbh, -avg_dbh))
sort(unique(os_dbh_in_plot$species))

# Overstory species w/measured DBH in or overhanging the plot
os_dbh_plot <- rbind(
      tag_dbh_plot %>% group_by(plotid, species, status, year) %>% 
            summarise(tot_ba_m2 = sum(tot_ba_m2), avg_ba_m2 = sum(tot_ba_m2)/sum(abundance),
                      abundance = sum(abundance)), 
      select(alt_dbh_plot, -tot_dbh, -avg_dbh))
```

@@

impt_vals <- rbind(tag_dbh_stem %>% filter(location == "In", dbh >= 2.0) %>% 
                         select(plotid, species, dbh, status, year), 
                   alt_dbh_stem) %>% 
      group_by(plotid, species, status, year) %>% 
      summarise(sp_abund = length(species), 
                sp_basal_area = sum(sum(pi*dbh^2/40000, na.rm = T))) %>% 
      group_by(plotid, status, year) %>% 
      mutate(total_abund = sum(sp_abund), 
             total_basal_area = sum(sp_basal_area), 
             imp_val =  
                   0.5 * ( (sp_abund / total_abund) + 
                                 (sp_basal_area / total_basal_area) ) )
summary(impt_vals)
impt_vals$plotid <- as.factor(impt_vals$plotid)
impt_vals$species <- as.factor(impt_vals$species)
impt_vals$year <- as.factor(impt_vals$year)
unique(impt_vals$plotid)
```

@@

# Total number of plots each overstory species occurred in at least once based on stems rooted in the plot
ggplot(os_dbh_in_plot %>% 
             filter(species != "unk1", species != "unknown sp.") %>% 
             group_by(year, species, status) %>% 
             summarise(occurrence = length(plotid)), 
       aes(species, occurrence, label = occurrence)) +
      geom_bar(stat = "identity") +
      geom_text(nudge_y = 3) +
      facet_grid(status ~ year) +
      ylab("# of plots") +
      ggtitle("Overstory Species Occurrence")

# Total number of living stems for each overstory species by year across all plots
ggplot(os_dbh_in_plot %>%
             filter(species != "unk1", species != "unknown sp.") %>% 
             group_by(year, species, status) %>% 
             summarise(abundance = sum(abundance)), 
       aes(species, abundance, label = abundance)) +
      geom_bar(stat = "identity") +
      facet_grid(status ~ year) +
      ylab("abundance") +
      ggtitle("Overstory Species Abundance") +
      geom_text(aes(vjust = 0), nudge_y = 10)

## same as above, but filtering out the super-abundant UMCA
ggplot(os_dbh_in_plot %>% 
             filter(species != "umca", species != "unk1", 
                    species != "unknown sp.") %>% 
             group_by(year, species, status) %>% 
             summarise(abundance = sum(abundance)), 
       aes(species, abundance, label = abundance)) +
      geom_bar(stat = "identity") +
      facet_grid(status ~ year) +
      ylab("abundance") +
      ggtitle("Overstory Species Abundance (minus UMCA)") +
      geom_text(aes(vjust = 0), nudge_y = 6)

# Total numbers only for tagged host species. I think for 'Dead' status it is probably only fair to look at tagged host species because I don't think the dead stems of untagged species were frequently recorded earlier in the study.
## abundance
ggplot(os_dbh_in_plot %>% 
             filter(species == "lide" | species == "quag" | species == "quch" |
                          species == "quke" | species == "quag x quwi" | 
                          species == "quke x quag" | species == "umca") %>%
             group_by(species, status, year) %>% 
             summarise(abundance = sum(abundance)),
       aes(species, abundance, label = abundance)) +
      geom_bar(stat = "identity") +
      facet_grid(status ~ year) +
      ylab("abundance") +
      ggtitle("Tagged Overstory Species Abundance") +
      geom_text(aes(vjust = 0), nudge_y = 6)

qusp_dbh_plot <- tag_dbh_stem %>% 
      filter(species == "quke" | species == "quag" | species == "quch") %>%
            group_by(plotid, species, status, year, sod_dead) %>% 
            summarise(avg_ba_m2 = mean(pi*dbh^2/40000, na.rm = T), 
                tot_ba_m2 = sum(pi*dbh^2/40000, na.rm = T),
                abundance = length(dbh))
ggplot(qusp_dbh_plot, aes(species, abundance, label = abundance)) +
      geom_bar(stat = "identity") +
      facet_grid(sod_dead ~ year) +
      ylab("abundance") +
      ggtitle("Quercus Species SOD Killed and Living Abundance") #+
      geom_text(nudge_y = 6)
```

#### Total basal area of tagged species rooted in the plot
```{r basal area tagged species}
ggplot(os_dbh_in_plot %>% 
             filter(species == "lide" | species == "quag" | species == "quch" |
                          species == "quke" | species == "quag x quwi" | 
                          species == "quke x quag" | species == "umca") %>%
             group_by(species, status, year) %>% 
             summarise(basal_area = round(sum(tot_ba_m2), digits = 4)),
       aes(species, basal_area, label = basal_area)) +
      geom_bar(stat = "identity") +
      facet_grid(status ~ year) +
      ylab("basal area (m^2)") +
      ggtitle("Tagged Overstory Species Basal Area") +
      geom_text(aes(vjust = 0), nudge_y = 3)

# boxplot of total basal area for tagged species
ggplot(os_dbh_in_plot %>% 
             filter(species == "lide" | species == "quag" | species == "quch" |
                          species == "quke" | species == "quag x quwi" | 
                          species == "quke x quag" | species == "umca"),
       aes(species, tot_ba_m2, label = plotid)) +
      geom_boxplot() +
      facet_grid(status ~ year) +
      ylab("basal area (m^2)") +
      ggtitle("Tagged Overstory Species Basal Area") +
      geom_text(nudge_y = .2)

# Sudden oak death mortality for QUAG, QUKE, QUCH
tag_dbh_stem$sod_dead[tag_dbh_stem$sod_dead==0] <- "alive"
tag_dbh_stem$sod_dead[tag_dbh_stem$sod_dead==1] <- "killed"
summary(tag_dbh_stem %>% 
      filter(species == "quke" | species == "quag" | species == "quch"))
qusp_dbh_plot <- tag_dbh_stem %>% 
      filter(species == "quke" | species == "quag" | species == "quch") %>%
            group_by(plotid, species, status, year, sod_dead) %>% 
            summarise(avg_ba_m2 = mean(pi*dbh^2/40000, na.rm = T), 
                tot_ba_m2 = sum(pi*dbh^2/40000, na.rm = T),
                abundance = length(dbh))

@@

ggplot(impt_vals %>% 
             filter(species == "lide" | species == "quag" | species == "quch" |
                          species == "quke" | species == "quag x quwi" | 
                          species == "quke x quag" | species == "umca"),
       aes(species, imp_val, label = plotid)) +
      geom_boxplot() +
      facet_grid(status ~ year) +
      ylab("importance value") +
      ggtitle("Tagged Overstory Species Importance Value") #+
      geom_text(nudge_y = .2)
```

@@

ggplot(shannons_os, aes(year, diversity, label = plotid)) +
      geom_boxplot() +
      # facet_grid(status ~ year) +
      ylab("Shannon's Diversity Index") +
      ggtitle("Overstory Species Diversity") #+
      geom_text(nudge_y = .2)

ggplot(pielous_os, aes(year, evenness, label = plotid)) +
      geom_boxplot() +
      # facet_grid(status ~ year) +
      ylab("Pielou's Evenness Index") +
      ggtitle("Overstory Species Evenness") #+
      geom_text(nudge_y = .2)
```
No difference in diversity across the entire plot network. No difference in average evenness, but evenness does appear to decrease for a subset of plots? Or, these plots are simply identified as outliers in 2014, but not in 2005. I am going to look more closely at those plots with an evenness index < 0.25 in the next chunk.

@@

#### Other Plots
```{r plotting, echo=F}
ggplot(data = os_dbh_in_plot,
       aes(species, tot_ba_m2, label = plotid)) +
      geom_boxplot() +
      facet_grid(status ~ year) +
      #geom_text() +
      ylab("Basal Area (m^2)")

@@

ggplot(data = os_dbh_in_plot,
       aes(species, abundance)) +
      geom_boxplot() +
      facet_grid(status ~ year) +
      #geom_text() +
      ylab("Abundance")

ggplot(os_dbh_in_plot %>% filter(status == "Alive"), aes(tot_ba_m2)) + 
      geom_histogram() +
      facet_grid(species ~ year)
ggplot(os_dbh_in_plot %>% filter(status == "Alive"), aes(avg_ba_m2)) + 
      geom_histogram() +
      facet_grid(species ~ year)
ggplot(os_dbh_in_plot %>% filter(status == "Alive"), aes(abundance)) + 
      geom_histogram() +
      facet_grid(species ~ year)

boxplot(tot_ba_m2 ~ year, 
        data = os_dbh_in_plot %>% filter(status == "Alive", species == "UMCA"),
        ylab = "m^2",
        main = "Live UMCA Basal Area")
boxplot(tot_ba_m2 ~ year, 
        data = os_dbh_in_plot %>% filter(status == "Dead", species == "UMCA"),
        ylab = "m^2",
        main = "Dead UMCA Basal Area")

boxplot(tot_ba_m2 ~ year, 
        data = os_dbh_in_plot %>% filter(status == "Alive", species == "QUAG"),
        ylab = "m^2",
        main = "Live QUAG Basal Area")
boxplot(tot_ba_m2 ~ year, 
        data = os_dbh_in_plot %>% filter(status == "Dead", species == "QUAG"),
        ylab = "m^2",
        main = "Dead QUAG Basal Area")

ggplot(data = basal_abund %>% filter(status == "Alive", species == "QUAG"),
       aes(year, tot_ba_m2, group = year)) +
      geom_boxplot()

boxplot(abundance ~ year, 
        data = basal_abund %>% filter(status == "Alive", species == "QUAG"),
        ylab = "Number of stems",
        main = "Live QUAG Abundance")
boxplot(tot_ba_m2 ~ year, 
        data = basal_abund %>% filter(status == "Dead", species == "QUAG"),
        ylab = "Number of stems",
        main = "Dead QUAG Abundance")
```

>>>>

# Overstory species data of tagged and untagged stems
tag_dbh_plot <- as.tbl(read.csv("analysis/data/tag-dbh-plot.csv"))
tag_dbh_plot
tag_dbh_plot$plotid <- tolower(tag_dbh_plot$plotid)
tag_dbh_plot$species <- tolower(tag_dbh_plot$species)
tag_dbh_plot <- rename(tag_dbh_plot, stem_status = status)

tag_dbh_stem <- as.tbl(read.csv("analysis/data/tag-dbh_0514-corrected.csv"))
tag_dbh_stem
tag_dbh_stem$plotid <- tolower(tag_dbh_stem$plotid)
tag_dbh_stem$species <- tolower(tag_dbh_stem$species)
tag_dbh_stem <- rename(tag_dbh_stem, stem_status = status)
tag_dbh_stem <- left_join(tag_dbh_stem, select(tagged_stems, plotid, cluster, species, tag, location, stem_status, year, sod_killed))

alt_dbh_plot <- as.tbl(read.csv("analysis/data/alt-dbh-plot.csv"))
alt_dbh_plot
alt_dbh_plot <- rename(alt_dbh_plot, stem_status = status)

alt_dbh_stem <- as.tbl(read.csv("analysis/data/alt-species-dbh-corrected.csv"))
alt_dbh_stem
alt_dbh_stem <- rename(alt_dbh_stem, stem_status = status)

all_stems <- as.tbl(read.csv("analysis/data/all_stems_corrected.csv"))
summary(all_stems)
      # rbind(select(tag_dbh_stem, plotid, species, dbh, status, year),
      #             alt_dbh_stem)
all_stems$plotid <- as.factor(all_stems$plotid)
all_stems$stem_status <- as.factor(all_stems$stem_status)
all_stems$year <- as.factor(all_stems$year)

@@

```{r recalculate plot data, echo=F}
# Recalculate tag-dbh-plot to exclude new large dead quag stem in 2014 at sugar05
filter(tag_dbh_stem, plotid == "sugar05", year == 2014)
tag_dbh_plot <- tag_dbh_stem %>% 
      filter(dbh >= 2.0, tag != 7794) %>% 
      group_by(plotid, species, year, stem_status, location) %>% 
      summarise(avg_ba_m2 = mean(pi*dbh^2/40000, na.rm = T), 
                tot_ba_m2 = sum(pi*dbh^2/40000, na.rm = T),
                abundance = length(dbh))
tag_dbh_plot <- ungroup(tag_dbh_plot)

# Overstory species w/measured DBH rooted in the plot
os_dbh_in_plot <- rbind(
      tag_dbh_plot %>% filter(location == "In") %>% 
            select(plotid, species, stem_status, year, everything(), -location), 
      select(alt_dbh_plot, -tot_dbh, -avg_dbh))
sort(unique(os_dbh_in_plot$species))

# Overstory species w/measured DBH in or overhanging the plot
os_dbh_plot <- rbind(
      tag_dbh_plot %>% group_by(plotid, species, stem_status, year) %>% 
            summarise(tot_ba_m2 = sum(tot_ba_m2), avg_ba_m2 = sum(tot_ba_m2)/sum(abundance),
                      abundance = sum(abundance)), 
      select(alt_dbh_plot, -tot_dbh, -avg_dbh))
```

@@

impt_vals <- rbind(tag_dbh_stem %>% filter(location == "In", dbh >= 2.0) %>% 
                         select(plotid, species, dbh, stem_status, year), 
                   alt_dbh_stem) %>% 
      group_by(plotid, species, stem_status, year) %>% 
      summarise(sp_abund = length(species), 
                sp_basal_area = sum(sum(pi*dbh^2/40000, na.rm = T))) %>% 
      group_by(plotid, stem_status, year) %>% 
      mutate(total_abund = sum(sp_abund), 
             total_basal_area = sum(sp_basal_area), 
             imp_val =  
                   0.5 * ( (sp_abund / total_abund) + 
                                 (sp_basal_area / total_basal_area) ) )
summary(impt_vals)
impt_vals$plotid <- as.factor(impt_vals$plotid)
impt_vals$species <- as.factor(impt_vals$species)
impt_vals$year <- as.factor(impt_vals$year)
unique(impt_vals$plotid)
```

@@

# Total number of plots each overstory species occurred in at least once based on stems rooted in the plot
ggplot(os_dbh_in_plot %>% 
             filter(species != "unk1", species != "unknown sp.") %>% 
             group_by(year, species, stem_status) %>% 
             summarise(occurrence = length(plotid)), 
       aes(species, occurrence, label = occurrence)) +
      geom_bar(stat = "identity") +
      geom_text(nudge_y = 3) +
      facet_grid(stem_status ~ year) +
      ylab("# of plots") +
      ggtitle("Overstory Species Occurrence")

# Total number of living stems for each overstory species by year across all plots
ggplot(os_dbh_in_plot %>%
             filter(species != "unk1", species != "unknown sp.") %>% 
             group_by(year, species, stem_status) %>% 
             summarise(abundance = sum(abundance)), 
       aes(species, abundance, label = abundance)) +
      geom_bar(stat = "identity") +
      facet_grid(stem_status ~ year) +
      ylab("abundance") +
      ggtitle("Overstory Species Abundance") +
      geom_text(aes(vjust = 0), nudge_y = 10)

## same as above, but filtering out the super-abundant UMCA
ggplot(os_dbh_in_plot %>% 
             filter(species != "umca", species != "unk1", 
                    species != "unknown sp.") %>% 
             group_by(year, species, stem_status) %>% 
             summarise(abundance = sum(abundance)), 
       aes(species, abundance, label = abundance)) +
      geom_bar(stat = "identity") +
      facet_grid(stem_status ~ year) +
      ylab("abundance") +
      ggtitle("Overstory Species Abundance (minus UMCA)") +
      geom_text(aes(vjust = 0), nudge_y = 6)

## select overstory species abundance, abundance ≥ 100 stems
ggplot(os_dbh_in_plot %>%
             filter(species == "umca" | species == "quag" | species == "quga" | species == "psme" | species == "arme" | species == "quke" | species == "quch") %>% 
             group_by(year, species, stem_status) %>% 
             summarise(abundance = sum(abundance)), 
       aes(species, abundance, label = abundance)) +
      geom_bar(stat = "identity") +
      facet_grid(stem_status ~ year, scales = "free") +
      ylab("abundance") +
      ggtitle("Overstory Species Abundance") +
      geom_text(aes(vjust = 0), nudge_y = 8) +
      theme_bw()

ggplot(os_dbh_in_plot %>%
             filter(species == "umca" | species == "quag" | species == "quga" | species == "psme" | species == "arme" | species == "quke" | species == "quch" | species == "sese") %>% 
             group_by(year, species, stem_status) %>% 
             summarise(tot_ba_m2 = round(sum(tot_ba_m2), 2)), 
       aes(species, tot_ba_m2, label = tot_ba_m2)) +
      geom_bar(stat = "identity") +
      facet_grid(stem_status ~ year, scales = "free") +
      ylab("basal area") +
      ggtitle("Overstory Species Basal Area") +
      geom_text(aes(vjust = 0), nudge_y = 1.5) +
      theme_bw()

# Total numbers only for tagged host species. I think for 'Dead' status it is probably only fair to look at tagged host species because I don't think the dead stems of untagged species were frequently recorded earlier in the study.
## abundance
ggplot(os_dbh_in_plot %>% 
             filter(species == "lide" | species == "quag" | species == "quch" |
                          species == "quke" | species == "umca") %>%
             group_by(species, stem_status, year) %>% 
             summarise(abundance = sum(abundance)),
       aes(species, abundance, label = abundance)) +
      geom_bar(stat = "identity") +
      facet_grid(stem_status ~ year) +
      ylab("abundance") +
      ggtitle("Tagged Overstory Species Abundance") +
      geom_text(aes(vjust = 0), nudge_y = 6)

qusp_dbh_plot <- tag_dbh_stem %>% 
      filter(species == "quke" | species == "quag" | species == "quch") %>%
            group_by(plotid, species, stem_status, year, sod_killed) %>% 
            summarise(avg_ba_m2 = mean(pi*dbh^2/40000, na.rm = T), 
                tot_ba_m2 = sum(pi*dbh^2/40000, na.rm = T),
                abundance = length(dbh))
qusp_dbh_plot <- ungroup(qusp_dbh_plot)
summary(qusp_dbh_plot)
filter(qusp_dbh_plot, is.na(sod_killed))
qusp_dbh_plot$sod_killed[is.na(qusp_dbh_plot$sod_killed)] <- "No"

ggplot(qusp_dbh_plot, aes(species, abundance, label = abundance)) +
      geom_bar(stat = "identity") +
      facet_grid(sod_killed ~ year, scales = "free") +
      ylab("abundance") +
      ggtitle("Quercus Species SOD Killed and Living Abundance") #+
      geom_text(nudge_y = 6)
```

#### Total basal area of tagged species rooted in the plot
```{r basal area tagged species}
ggplot(os_dbh_in_plot %>% 
             filter(species == "lide" | species == "quag" | species == "quch" |
                          species == "quke" | species == "quag x quwi" | 
                          species == "quke x quag" | species == "umca") %>%
             group_by(species, stem_status, year) %>% 
             summarise(basal_area = round(sum(tot_ba_m2), digits = 4)),
       aes(species, basal_area, label = basal_area)) +
      geom_bar(stat = "identity") +
      facet_grid(stem_status ~ year) +
      ylab("basal area (m^2)") +
      ggtitle("Tagged Overstory Species Basal Area") +
      geom_text(aes(vjust = 0), nudge_y = 3)

# boxplot of total basal area for tagged species
ggplot(os_dbh_in_plot %>% 
             filter(species == "lide" | species == "quag" | species == "quch" |
                          species == "quke" | species == "quag x quwi" | 
                          species == "quke x quag" | species == "umca"),
       aes(species, tot_ba_m2, label = plotid)) +
      geom_boxplot() +
      facet_grid(stem_status ~ year) +
      ylab("basal area (m^2)") +
      ggtitle("Tagged Overstory Species Basal Area") +
      geom_text(nudge_y = .2)

# Sudden oak death mortality for QUAG, QUKE, QUCH
tag_dbh_stem$sod_dead[tag_dbh_stem$sod_dead==0] <- "alive"
tag_dbh_stem$sod_dead[tag_dbh_stem$sod_dead==1] <- "killed"
summary(tag_dbh_stem %>% 
      filter(species == "quke" | species == "quag" | species == "quch"))
qusp_dbh_plot <- tag_dbh_stem %>% 
      filter(species == "quke" | species == "quag" | species == "quch") %>%
            group_by(plotid, species, stem_status, year, sod_dead) %>% 
            summarise(avg_ba_m2 = mean(pi*dbh^2/40000, na.rm = T), 
                tot_ba_m2 = sum(pi*dbh^2/40000, na.rm = T),
                abundance = length(dbh))

@@

ggplot(impt_vals %>% 
             filter(species == "lide" | species == "quag" | species == "quch" |
                          species == "quke" | species == "quag x quwi" | 
                          species == "quke x quag" | species == "umca"),
       aes(species, imp_val, label = plotid)) +
      geom_boxplot() +
      facet_grid(stem_status ~ year) +
      ylab("importance value") +
      ggtitle("Tagged Overstory Species Importance Value") #+
      geom_text(nudge_y = .2)
```

@@

ggplot(shannons_os, aes(year, diversity, label = plotid)) +
      geom_boxplot() +
      # facet_grid(stem_status ~ year) +
      ylab("Shannon's Diversity Index") +
      ggtitle("Overstory Species Diversity") #+
      geom_text(nudge_y = .2)

ggplot(pielous_os, aes(year, evenness, label = plotid)) +
      geom_boxplot() +
      # facet_grid(stem_status ~ year) +
      ylab("Pielou's Evenness Index") +
      ggtitle("Overstory Species Evenness") #+
      geom_text(nudge_y = .2)
```
No difference in diversity across the entire plot network. No difference in average evenness, but evenness does appear to decrease for a subset of plots? Or, these plots are simply identified as outliers in 2014, but not in 2005. I am going to look more closely at those plots with an evenness index < 0.25 in the next chunk.

@@

#### Other Plots
```{r plotting, echo=F}
ggplot(data = os_dbh_in_plot,
       aes(species, tot_ba_m2, label = plotid)) +
      geom_boxplot() +
      facet_grid(stem_status ~ year) +
      #geom_text() +
      ylab("Basal Area (m^2)")

@@

ggplot(data = os_dbh_in_plot,
       aes(species, abundance)) +
      geom_boxplot() +
      facet_grid(stem_status ~ year) +
      #geom_text() +
      ylab("Abundance")

ggplot(os_dbh_in_plot %>% filter(stem_status == "Alive"), aes(tot_ba_m2)) + 
      geom_histogram() +
      facet_grid(species ~ year)
ggplot(os_dbh_in_plot %>% filter(stem_status == "Alive"), aes(avg_ba_m2)) + 
      geom_histogram() +
      facet_grid(species ~ year)
ggplot(os_dbh_in_plot %>% filter(stem_status == "Alive"), aes(abundance)) + 
      geom_histogram() +
      facet_grid(species ~ year)

boxplot(tot_ba_m2 ~ year, 
        data = os_dbh_in_plot %>% filter(stem_status == "Alive", species == "UMCA"),
        ylab = "m^2",
        main = "Live UMCA Basal Area")
boxplot(tot_ba_m2 ~ year, 
        data = os_dbh_in_plot %>% filter(stem_status == "Dead", species == "UMCA"),
        ylab = "m^2",
        main = "Dead UMCA Basal Area")

boxplot(tot_ba_m2 ~ year, 
        data = os_dbh_in_plot %>% filter(stem_status == "Alive", species == "QUAG"),
        ylab = "m^2",
        main = "Live QUAG Basal Area")
boxplot(tot_ba_m2 ~ year, 
        data = os_dbh_in_plot %>% filter(stem_status == "Dead", species == "QUAG"),
        ylab = "m^2",
        main = "Dead QUAG Basal Area")

ggplot(data = basal_abund %>% filter(stem_status == "Alive", species == "QUAG"),
       aes(year, tot_ba_m2, group = year)) +
      geom_boxplot()

boxplot(abundance ~ year, 
        data = basal_abund %>% filter(stem_status == "Alive", species == "QUAG"),
        ylab = "Number of stems",
        main = "Live QUAG Abundance")
boxplot(tot_ba_m2 ~ year, 
        data = basal_abund %>% filter(stem_status == "Dead", species == "QUAG"),
        ylab = "Number of stems",
        main = "Dead QUAG Abundance")
```
